GVN-Hoist: Hoisting Computations from Branches

### 2016-08-07 hoist.tex
overview

Hoisting also reduces critical path length of execution in out of
order machines (but not in sequential machines), by exposing ILP
before the conditional where the instruction was hoisted.

@@

In this program the computations of tmax and tmin and identical in
both the branches but they cannot be evaluated before inv. Since inv
depends on a division operation which is generally more expensive than
the addition, subtraction and multiplication operations as required to
evaluate tmax and tmin, the total latency of computation across each
branch is:

@@

In this code the two subtractions and the div operations can execute
in parallel. So the total number of cycles will be O(div) + O(mul)
since O(div) is usually greater than O(sub)

Of course, a sinking optimization could just sink the computation of
both tmax and tmin, and since the final operation is an addition
(asociative under fast math), the entire if-else code would go away.

>>>>

Code hoisting can also reduce the critical path length of execution in out of
order machines. As more instructios are available at the hoisting point, the
hardware has more instructions to reorder. Following example illustrates how
hoisting can improve performance by exposing more ILP.

@@

In this program the computations of tmax and tmin and identical in
both the branches but they cannot be evaluated before inv. Since inv
depends on a division operation which is generally more expensive than
the addition, subtraction and multiplication operations as required to
evaluate tmax and tmin. The total latency of computation across each
branch is:

@@

In this code the two subtractions and the div operations can execute
in parallel. So the total number of cycles will be max(O(div), O(sub)) + O(mul)
= O(div) + O(mul); since O(div) is usually greater than O(sub)

Of course, a partial redundancy elimination pass could just remove the entire
if-block because final operation is an addition (asociative under fast math).
